Accuracy and precision of zero-heat-flux temperature monitoring: A systematic review and meta-analysis

### 2019-12-04 manuscript/manuscript.Rmd
removed tidyverse call for specific packages

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(knitr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(gt)
source("loa_maker.R")
source("meta.R")
```

@@

```{r meta-analysis-prep, include=FALSE}
data <- data %>%
  mutate(c = N/n)

@@

data <- data %>% 
  mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
         corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
                        )
        )

data <- data %>% 
  mutate(V_bias = s2/n)

data <- data %>% 
  mutate(logs2 = log(s2)+1/(n-1))

data <- data %>% 
  mutate(V_logs2 = 2/(n-1))
```

@@

data_NPA <- data %>% 
  filter(comparison == "NPA")

data_SL <- data %>% 
  filter(comparison == "Sublingual")

#eshragi overall
data_core <- data %>% 
  filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

data_core_op <- data %>% #eshragi intraop
    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter (clinical_setting=="Intraoperative")

data_core_icu <- data %>% #eshragi postop
      filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")

@@

data_core_lowrisk <- data_core %>% #eshragi overall
  filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")

@@

data_conflict <- data_core %>% 
  filter(`Funding/equipment/conflict with ZHF company` == "No")

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=2)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m)
out

@@

```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
include_graphics("gofer_core.png")
```

@@

```{r table-1, layout="l-page-outset", include=params$distill}
library(kableExtra)
  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>%
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>%
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```

>>>>

```{r echo=FALSE, include=FALSE}
library(magrittr)
source("loa_maker.R")
source("meta.R")
```

@@

```{r meta-analysis-prep, include=FALSE}
data <- data %>%
  dplyr::mutate(c = N/n)

@@

data <- data %>% 
  dplyr::mutate(s2 = dplyr::case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
         corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
                        )
        )

data <- data %>% 
  dplyr::mutate(V_bias = s2/n)

data <- data %>% 
  dplyr::mutate(logs2 = log(s2)+1/(n-1))

data <- data %>% 
  dplyr::mutate(V_logs2 = 2/(n-1))
```

@@

data_NPA <- data %>% 
  dplyr::filter(comparison == "NPA")

data_SL <- data %>% 
  dplyr::filter(comparison == "Sublingual")

#eshragi overall
data_core <- data %>% 
  dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  dplyr::filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

data_core_op <- data %>% #eshragi intraop
    dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  dplyr::filter (clinical_setting=="Intraoperative")

data_core_icu <- data %>% #eshragi postop
      dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  dplyr::filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")

@@

data_core_lowrisk <- data_core %>% #eshragi overall
  dplyr::filter(RoB_selection == "low" & RoB_spoton == "low" & RoB_comparator == "low" & RoB_flow =="low")

@@

data_conflict <- data_core %>% 
  dplyr::filter(`Funding/equipment/conflict with ZHF company` == "No")

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=2)
out <- out %>% 
  dplyr::mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  dplyr::mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
  dplyr::mutate(Studies = length(unique(group$Study))) %>% 
  dplyr::select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  dplyr::rename("Comparisons" = m)
out

@@

```{r fig-2, preview=TRUE, layout="l-screen-inset", fig.align="center", fig.cap="Graphical overview of findings for the primary analysis", echo=FALSE, fig.path="", include=params$distill}
knitr::include_graphics("gofer_core.png")
```

@@

```{r table-1, layout="l-page-outset", include=params$distill}
  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- dplyr::bind_rows(ma, .id="Comparison")
df %>% 
  dplyr::rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt::gt() %>%
  gt::tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>%
  gt::tab_spanner(
    label = "Population limits of agreement",
    columns = gt::vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```
